Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2019-12-30 manuscript/main.tex
Add equation for weighted Hamming distance, define D0 constant

The weighted Hamming distance to the future of each strain was calculated from the strain's HA amino acid sequence and the frequencies and sequences of the corresponding population one year in the future.
\jhc{Add equation for weighted Hamming distance here.}

@@

We estimated antigenic drift for each strain using either genetic or HI data.
To estimate antigenic drift with genetic data, we implemented the cross-immunity metric originally defined by {\L}uksza and L\"assig \cite{Luksza:2014hj}.
Briefly, for each pair of strains in adjacent seasons, we counted the number of amino acid differences between the strains' HA sequences at 49 epitope sites.
The one-based coordinates of these sites relative to the start of the HA1 segment were 50, 53, 54, 121, 122, 124, 126, 131, 133, 135, 137, 142, 143, 144, 145, 146, 155, 156, 157, 158, 159, 160, 163, 164, 172, 173, 174, 186, 188, 189, 190, 192, 193, 196, 197, 201, 207, 213, 217, 226, 227, 242, 244, 248, 275, 276, 278, 299, and 307.
We limited pairwise comparisons to all strains sampled within the last five years from each timepoint.
For each individual strain $i$ at each timepoint $t$, we estimated that strain's ability to escape cross-immunity by summing the exponentially-scaled epitope distances between previously circulating strains and the given strain as follows.

>>>>

We calculated the weighted Hamming distance to the future of each strain from the strain's HA amino acid sequence and the frequencies and sequences of the corresponding population one year in the future.
Specifically, the distance between any strain $i$ from timepoint $t$ to the future timepoint $u$ was the Hamming distance, $h$, between strain $i$'s amino acid sequence, $s_{i}$, each future strain $j$'s amino acid sequence, $s_{j}$, and the frequency of strain $j$ in the future timepoint, $x_{j}(u)$.

\begin{equation}
  d_{i}(u) = \sum_{j \in s(u)}{x_{j}(u)h(s_{i}, s_{j})}
  \label{equation_observed_weighted_distance_to_future}
\end{equation}

We calculated the estimated distance to the future for live forecasts with the same approach, replacing the observed future population frequencies and sequences with the estimated population based on our models.

\begin{equation}
  d_{i}(\hat{u}) = \sum_{j \in s(\hat{u})}{x_{j}(\hat{u})h(s_{i}, s_{j})}
  \label{equation_estimated_weighted_distance_to_future}
\end{equation}

@@

We estimated antigenic drift for each strain using either genetic or HI data.
To estimate antigenic drift with genetic data, we implemented the cross-immunity metric originally defined by {\L}uksza and L\"assig \cite{Luksza:2014hj}.
Briefly, for each pair of strains in adjacent seasons, we counted the number of amino acid differences between the strains' HA sequences at 49 epitope sites.
The one-based coordinates of these sites relative to the start of the HA1 segment were 50, 53, 54, 121, 122, 124, 126, 131, 133, 135, 137, 142, 143, 144, 145, 146, 155, 156, 157, 158, 159, 160, 163, 164, 172, 173, 174, 186, 188, 189, 190, 192, 193, 196, 197, 201, 207, 213, 217, 226, 227, 242, 244, 248, 275, 276, 278, 299, and 307.
We limited pairwise comparisons to all strains sampled within the last five years from each timepoint.
For each individual strain $i$ at each timepoint $t$, we estimated that strain's ability to escape cross-immunity by summing the exponentially-scaled epitope distances between previously circulating strains and the given strain as in Equation~\ref{equation_epitope_cross_immunity}.
We defined the constant $D_{0} = 14$, as in the original definition of cross-immunity \cite{Luksza:2014hj}.
